\textbf{COMP0086 Summative Assignment}

### 2022-11-08 submission.tex
reorganising file structure

\newpage
\item[(d\&e)] The Python code for MLE and MAP:
\lstinputlisting[language=Python, caption: MLE and MAP Implementation,]{src/solutions/q1.py}
\newpage
%  \begin{figure}[h]
%  \centering
%  \includegraphics[scale=0.5]{outputs/python/q1/q1d}
%  \caption{ML parameters}
%  \label{fig:1d}
%  \end{figure}
%  \begin{figure}[h]
%  \centering
%  \includegraphics[scale=0.5]{outputs/python/q1/q1e}
%  \caption{MAP parameters}
%  \label{fig:1e}
%  \end{figure}

Displaying the learned parameters:
\begin{figure}[h]
\centering
\begin{minipage}{0.5\textwidth}
  \centering
  \includegraphics[scale=0.5]{outputs/python/q1/q1d}
  \caption{ML parameters}
  \label{fig:1d}
\end{minipage}%
\begin{minipage}{0.5\textwidth}
  \centering
  \includegraphics[scale=0.5]{outputs/python/q1/q1e}
  \caption{MAP parameters}
  \label{fig:1e}
\end{minipage}
\end{figure}

@@

  \end{figure}
  \begin{figure}[h]
  \centering
  \includegraphics[scale=0.5]{outputs/python/q1/q1e-mle-vs-map}
  \caption{$\hat{\textbf{p}}^{MAP}-\hat{\textbf{p}}^{MLE}$}
  \label{fig:1e}
  \end{figure}

@@

\begin{center}
\begin{tabular}{l|c}%
 \bfseries $i$ & \bfseries$ P(M_i|\mathcal{D})$% specify table head
\csvreader[head to column names]{outputs/python/q2/q2c.csv}{}% use head of csv as column names
{\\\hline\csvcoli&\csvcolii}% specify your coloumns here
\end{tabular}
\end{center}

>>>>

\newpage
\item[(d\&e)] The Python code for MLE and MAP:
\lstinputlisting[language=Python, caption: MLE and MAP Implementation,]{src/solutions/q1.py}
\newpage
%  \begin{figure}[h]
%  \centering
%  \includegraphics[scale=0.5]{outputs/q1/q1d}
%  \caption{ML parameters}
%  \label{fig:1d}
%  \end{figure}
%  \begin{figure}[h]
%  \centering
%  \includegraphics[scale=0.5]{outputs/q1/q1e}
%  \caption{MAP parameters}
%  \label{fig:1e}
%  \end{figure}

Displaying the learned parameters:
\begin{figure}[h]
\centering
\begin{minipage}{0.5\textwidth}
  \centering
  \includegraphics[scale=0.5]{outputs/q1/q1d}
  \caption{ML parameters}
  \label{fig:1d}
\end{minipage}%
\begin{minipage}{0.5\textwidth}
  \centering
  \includegraphics[scale=0.5]{outputs/q1/q1e}
  \caption{MAP parameters}
  \label{fig:1e}
\end{minipage}
\end{figure}

@@

  \end{figure}
  \begin{figure}[h]
  \centering
  \includegraphics[scale=0.5]{outputs/q1/q1e-mle-vs-map}
  \caption{$\hat{\textbf{p}}^{MAP}-\hat{\textbf{p}}^{MLE}$}
  \label{fig:1e}
  \end{figure}

@@

\begin{center}
\begin{tabular}{l|c}%
 \bfseries $i$ & \bfseries$ P(M_i|\mathcal{D})$% specify table head
\csvreader[head to column names]{outputs/q2/q2c.csv}{}% use head of csv as column names
{\\\hline\csvcoli&\csvcolii}% specify your coloumns here
\end{tabular}
\end{center}
